Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-03 Paper/main.tex
minor wording change

In 2000, Kosovic and Curry \cite{Kosovic2000} used an LES simulation with a nonlinear SGS
model containing backscatter to favorably compare to the \fxnote{[Nate: define BASE]} BASE measurements, showing that
the SBL could reach a quasi steady-state. They also showed good agreement with the Nieustadt
analytical model. In the same year, Saiki et al. \cite{Saiki2000} simulated an SBL with
a strong capping inversion at z=500m, producing reasonable surface layer profiles and
identifying a need for SBL specific SGS models. Beare and MacVean \cite{Beare2004}
presented the first grid-focused work on LES of the SBL, using grids with deltas
between 2m and 12.5m, finding significant variation between grid sizes. The inclusion
of a backscatter model resulted in significant variation at a 6.25m resolution, but
very little at a 2m resolution. Basu et al. \cite{Basu2005} published a set of
turbulence statistics, measurements, and LES simulations in support
of the viability of Nieustadt's local scaling hypothesis under very stable
conditions. Jimenez and Cuxart \cite{Jimenez2005} set out to quantify the range
for which standard SGS models, using the Kolmogorov theory for dissipation, were
valid for increasingly stable flows. They found the model to perform adequately
for weakly stable, and some moderately stable flow regimes.

>>>>

In 2000, Kosovic and Curry \cite{Kosovic2000} used an LES simulation
with a nonlinear SGS model containing backscatter to favorably compare
to the Beaufort Sea Arctic Stratus Experiment (BASE) measurements,
showing that the SBL could reach a quasi steady-state. They also
showed good agreement with the Nieustadt analytical model. In the same
year, Saiki et al. \cite{Saiki2000} simulated an SBL with
a strong capping inversion at z=500m, producing reasonable surface layer profiles and
identifying a need for SBL specific SGS models. Beare and MacVean \cite{Beare2004}
presented the first grid-focused work on LES of the SBL, using grids with deltas
between 2m and 12.5m, finding significant variation between grid sizes. The inclusion
of a backscatter model resulted in significant variation at a 6.25m resolution, but
very little at a 2m resolution. Basu et al. \cite{Basu2005} published a set of
turbulence statistics, measurements, and LES simulations in support
of the viability of Nieustadt's local scaling hypothesis under very stable
conditions. Jimenez and Cuxart \cite{Jimenez2005} set out to quantify the range
for which standard SGS models, using the Kolmogorov theory for dissipation, were
valid for increasingly stable flows. They found the model to perform adequately
for weakly stable, and some moderately stable flow regimes.
